---
title: "Data Reanalysis Notebook"
output: 
  html_notebook:
    theme: paper
    toc: yes
    toc_float: yes
---

# Load Packages {.tabset}

## Haven
```{r}
# This package teaches R how to import SPSS files
if (!require(haven)){
  install.packages("haven", dependencies = TRUE)
  require(haven)
}
```

## Tidyverse
```{r}
# This package has a million useful functions for tidying, cleaning, and reshaping data
if (!require(tidyverse)){
  install.packages("tidyverse", dependencies = TRUE)
  require(tidyverse)
}
```

## Psych
```{r}
# This  package has useful functions for psychologists like correlation and creating composite variables
if (!require(psych)){
  install.packages("psych", dependencies = TRUE)
  require(psych)
}
```
# Import Data {.tabset}

## 2015 UK data
```{r}
UKdataset <- read_sav("2015 UK Undergraduates.sav")
```
## 2017 Florida Registered Voters
```{r}
FLdataset <- read_sav("2017 Registered Florida Voters.sav")
```
## 2018 US mTurk workers
```{r}
# Load the data
MTURKdataset <- read_sav("2018 mTurk Workers.sav")
```
```{r}
# Recode the gender variable
MTURKdataset$gender <- case_when(str_sub(MTURKdataset$Q107, 1, 1) == "f" | str_sub(MTURKdataset$Q107, 1, 1) == "F" ~ "female",
                                 str_sub(MTURKdataset$Q107, 1, 1) == "m" | str_sub(MTURKdataset$Q107, 1, 1) == "M" ~ "male",
                                 TRUE ~ as.character(MTURKdataset$Q107))

# Recode the race variable
MTURKdataset$race <- case_when(str_sub(MTURKdataset$Q109.2, 1, 1) == "w" | str_sub(MTURKdataset$Q109.2, 1, 1) == "W" | str_sub(MTURKdataset$Q109.2, 1, 1) == "c" | str_sub(MTURKdataset$Q109.2, 1, 1) == "C" ~ "White",
                                 TRUE ~ as.character(MTURKdataset$Q109.2))
```

# Correlation Tables {.tabset}

## 2015 UK data {.tabset}

### White participants
```{r}
(UKdataset %>%
  filter (WhiteOnlyFilter == 1) %>%
  select (AW_B, AWM_BM, AWF_BF) %>%  
  corr.test(y = NULL, use = "pairwise", method="pearson", adjust="holm", alpha=.05, ci=TRUE) -> UKWhiteCorrs)
```
### White male participants
```{r}
(UKdataset %>%
  filter (WhiteOnlyFilter == 1,
          PGender == "male") %>%
  select (AW_B, AWM_BM, AWF_BF) %>%  
  corr.test(y = NULL, use = "pairwise", method="pearson", adjust="holm", alpha=.05, ci=TRUE) -> UKWHITEMaleCorrs)
```
### White female participants
```{r}
(UKdataset %>%
  filter (WhiteOnlyFilter == 1,
          PGender == "female") %>%
  select (AW_B, AWM_BM, AWF_BF) %>%  
  corr.test(y = NULL, use = "pairwise", method="pearson", adjust="holm", alpha=.05, ci=TRUE) -> UKWhiteFemaleCorrs)
```
## 2017 Florida Registered Voters {.tabset}
### White participants
```{r}
(FLdataset %>%
  filter (racew == 1) %>%
  select (AttitudeWhiteminusBlack, AttitudeWMminusBM, AttitudeWFminusBF) %>%  
  corr.test(y = NULL, use = "pairwise", method="pearson", adjust="holm", alpha=.05, ci=TRUE) -> FLWhiteCorrs)
```
### White male participants
```{r}
(FLdataset %>%
  filter (racew == 1,
          sex2 == 1) %>%
  select (AttitudeWhiteminusBlack, AttitudeWMminusBM, AttitudeWFminusBF) %>%  
  corr.test(y = NULL, use = "pairwise", method="pearson", adjust="holm", alpha=.05, ci=TRUE) -> FLWhiteMaleCorrs)
```
### White female participants
```{r}
(FLdataset %>%
  filter (racew == 1,
          sex2 == 2) %>%
  select (AttitudeWhiteminusBlack, AttitudeWMminusBM, AttitudeWFminusBF) %>%  
  corr.test(y = NULL, use = "pairwise", method="pearson", adjust="holm", alpha=.05, ci=TRUE) -> FLFemaleCorrs)
```
## 2018 US mTurk workers {.tabset}
### White participants
```{r}
(MTURKdataset %>%
  filter (race == "White") %>%
  select (Predjudice_White_Black, Predjudice_WhiteMen_BlackMen, Predjudice_WhiteWomen_BlackWomen) %>%  
  corr.test(y = NULL, use = "pairwise", method="pearson", adjust="holm", alpha=.05, ci=TRUE) -> MTURKWhiteCorrs)
```
### White male participants
```{r}
(MTURKdataset %>%
  filter (race == "White",
          gender == "male") %>%
  select (Predjudice_White_Black, Predjudice_WhiteMen_BlackMen, Predjudice_WhiteWomen_BlackWomen) %>%  
  corr.test(y = NULL, use = "pairwise", method="pearson", adjust="holm", alpha=.05, ci=TRUE) -> MTURKWhiteMaleCorrs)
```
### White female participants
```{r}
(MTURKdataset %>%
  filter (race == "White",
          gender == "female") %>%
  select (Predjudice_White_Black, Predjudice_WhiteMen_BlackMen, Predjudice_WhiteWomen_BlackWomen) %>%  
  corr.test(y = NULL, use = "pairwise", method="pearson", adjust="holm", alpha=.05, ci=TRUE) -> MTURKWhiteFemaleCorrs)
```
# Test of correlation differences {.tabset}
## 2015 UK data {.tabset}
### White participants
```{r}
paired.r(xy = UKWhiteCorrs$r[1,2], xz = UKWhiteCorrs$r[1,3], yz = UKWhiteCorrs$r[2,3], n = 77, n2=NULL,twotailed=TRUE)
```
### White male participants
```{r}
paired.r(xy = UKWHITEMaleCorrs$r[1,2], xz = UKWHITEMaleCorrs$r[1,3], yz = UKWHITEMaleCorrs$r[2,3], n = 10, n2=NULL,twotailed=TRUE)
```
### White female participants
```{r}
paired.r(xy = UKWhiteFemaleCorrs$r[1,2], xz = UKWhiteFemaleCorrs$r[1,3], yz = UKWhiteFemaleCorrs$r[2,3], n = 67, n2=NULL,twotailed=TRUE)
```
## 2017 Registered Florida Voters {.tabset}
### White participants
```{r}
paired.r(xy = FLWhiteCorrs$r[1,2], xz = FLWhiteCorrs$r[1,3], yz = FLWhiteCorrs$r[2,3], n = 180, n2=NULL,twotailed=TRUE)
```
### White male participants
```{r}
paired.r(xy = FLWhiteMaleCorrs$r[1,2], xz = FLWhiteMaleCorrs$r[1,3], yz = FLWhiteMaleCorrs$r[2,3], n = 92, n2=NULL,twotailed=TRUE)
```
### White female participants
```{r}
paired.r(xy = FLFemaleCorrs$r[1,2], xz = FLFemaleCorrs$r[1,3], yz = FLFemaleCorrs$r[2,3], n = 88, n2=NULL,twotailed=TRUE)
```
## 2018 US mTurk Workers {.tabset}
### White participants
```{r}
paired.r(xy = MTURKWhiteCorrs$r[1,2], xz = MTURKWhiteCorrs$r[1,3], yz = MTURKWhiteCorrs$r[2,3], n = 138, n2=139,twotailed=TRUE)
```
### White male participants
```{r}
paired.r(xy = MTURKWhiteMaleCorrs$r[1,2], xz = MTURKWhiteMaleCorrs$r[1,3], yz = MTURKWhiteMaleCorrs$r[2,3], n = 54, n2=55,twotailed=TRUE)
```
### White female participants
```{r}
paired.r(xy = MTURKWhiteFemaleCorrs$r[1,2], xz = MTURKWhiteFemaleCorrs$r[1,3], yz = MTURKWhiteFemaleCorrs$r[2,3], n = 83, n2=84,twotailed=TRUE)
```


